### 2018-10-17 tex/model.tex
SongTao revision.

In this chapter, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
FRQ model quantifies computing and I/O resources and displays them in time dimension. According to FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG framework, hardware environment, and so on. Therefore FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance. We will first introduce FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use FRQ model to describe three different computation job and analyze their performance. In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
The current distributed data parallel computing frameworks mostly use \textit{Directed acyclic graphs} (DAGs) to describe computation logic. A shuffle phase is required between each adjacent DAG computation phase. In order to better analyze the relationship between the computation phase and the shuffle phase, we propose FRQ model. After quantifying computing and I/O resources, FRQ model is able to describe different resource scheduling strategies. For convenience, we introduce FRQ model by taking a simple MapReduce job as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. FRQ model has five input parameters:
\begin{itemize}
	\item Input Data Size \((D)\): The data size of the computation phase.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase using the current computation resources. The number of rounds depends on the current computation resources and the settings of the computation job. Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the map phase consists of 200 map tasks. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
    The computation speed for each computation phase. The computation speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
    Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
\end{itemize}

@@

For shuffle-heavy computing jobs, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\). Improving I/O speed is a effective way to reduce shuffle time. Another optimization method is to use the idle I/O resources in the map phase for pre-fetching (see Figure \ref{fig:model_basic}). Both of the above methods can effectively reduce \(T_{P\_Shuffle}\). When using FRQ model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework. Different computing frameworks may use different resource scheduling strategies. FRQ model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.

@@

The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a naive scheduling strategy. As shown in Figure \ref{fig:model_original}, FRQ model describes a MapReduce job that is fully serially executed. The overlap time between the shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\). Therefore, the overhead of the reduce phase is 0. But since shuffle and computation are serial execution, the total execution time of a job is different from the above:
\begin{equation}
\label{equation_Tjob2}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
\end{aligned}
\end{equation}
Apache Spark uses this scheduling strategy by default. Due to serialization, the I/O resource is idle during the reduce phase and map phase. The scheduling strategy is simple and has a lot of room for optimization.

Figure \ref{fig:model_hadoop} shows one of the optimization methods. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase will increase (according to equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}). The execution time of the shuffle phase is hidden in the reduce phase. This scheduling strategy is used by Hadoop MapReduce. After analyzing this model, we believe that this strategy will be more efficient than the above serial strategy in the same situation. Meanwhile, we found that the I/O resource in the map phase is still idle. This scheduling strategy can be optimized.

@@

Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources. We intuitively think that we can also overlap shuffle phase one and map phases. We implemented this idea with SCache.
Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4). SCache starts pre-fetching and pre-scheduling in the map phase. This scheduling strategy can make better use of resources and avoid the I/O resource being idle in the map phase. According to the design of SCache pre-fetching, we found that using FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

\begin{enumerate}
    \item 
    \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1}): 
	The meaning of \(V_{Map} \times R\) is the speed at which shuffle data is generated. The meaning of the inequality is that the speed of generating shuffle data(\(V_{Map} \times R\)) is greater than or equal to the shuffle speed(\(V_{Shuffle}\)). When the Round1 of the map phase ends, the SCache starts shuffling data until the end of the shuffle phase. Due to shuffle speed is slower, the shuffle phase is uninterrupted. SCache transmit the shuffle data generated in the last round of map phase during the reduce phase. Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase:
	\begin{equation}
		\label{equation_Tpshuffle1}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N}
		\end{aligned}
	\end{equation}

    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2}): 
	When the speed of generating shuffle data (\(V_{Map} \times R\)) is less than the shuffle speed (\(V_{Shuffle}\)), SCache needs to wait for shuffle data to be generated. As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each Round. Thus \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase:
	\begin{equation}
		\label{equation_Tpshuffle2}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} \times \frac{1}{N}
		\end{aligned}
	\end{equation}
\end{enumerate}

@@

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in FRQ model}
\label{table1}
\centering
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
\hline
 &
\(D\) &	
\(R\) &	
\(N\) &	
\(V_{Map}\) &	
\(V_{Reduce}\) &	
\(V_{Shuffle}\) &	
\(K\) &	
\(T_{Map}\) &	
\(T_{Shuffle}\) &	
\(T_{P\_Shuffle}\) &
\(T_{Reduce}\) & 
\(T_{Job}\) & 
\(Exp T_{Job}\) &
\(Error\)\\

@@

\renewcommand{\arraystretch}{1.3}
\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in FRQ model}
\label{table2}
\centering
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
\hline
 &
\(D\) &	
\(R\) &	
\(N\) &	
\(V_{Map}\) &	
\(V_{Reduce}\) &	
\(V_{Shuffle}\) &	
\(K\) &	
\(T_{Map}\) &	
\(T_{Shuffle}\) &	
\(T_{P\_Shuffle}\) &
\(T_{Reduce}\) & 
\(T_{Job}\) & 
\(Exp T_{Job}\) &
\(Error\)\\

@@

\subsection{Model Verification}\label{model_verification}
In order to verify FRQ model, we run experiments on two environments. The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Section \ref{stepup}. Another environment is in our lab. Our in-house environment has 4 nodes and each node has 128GB and 32 CPUs. To simplify the calculation of the FRQ model, we use Hadoop MapReduce as a framework and use Terasort as a experimental application. We deployed Hadoop with SCache and without SCache in both environments.

Table \ref{table1} shows the calculational results of FRQ model in the in-house environment. Workload is from 16 GB to 64 GB. \(D\) and \(N\) are set according to the application parameters. \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are calculated based on experimental results. K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase in the case of SCache. The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. In the case of SCache, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}. In the case of Legacy, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}). \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\). The formula of \(Error\) is:
\begin{equation}
	\label{equation_error}
	\begin{aligned}
		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
	\end{aligned}
\end{equation}

Table \ref{table2} shows the calculational results of FRQ model in Amazon EC2 environment. \(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices. We also set K to the same empirical value. The formulas in the table are all the same except \(T_{P\_Shuffle}\). In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2}(\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}. In the previous case, \(T_{P\_Shuffle}\) is still euqal to \(T_{Shuffle}\).

@@

In order to verify the above-mentioned two cases when using SCache, we monitor network utilization and plot it in Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment. The network utilization remains high until shuffle phase is complete. This situation is consistent with Figure \ref{fig:model_scache1}. Figure \ref{fig:hadoop_net2} shows the utilization in Amazon EC2 environment. 
The network utilization has 5 regular peaks. This situation is also consistent with Figure \ref{fig:model_scache2}. Therefore, we believe that FRQ model is able to accurately describe the performance of a framework with SCache.

In terms of accuracy, the experimental values are all greater than the calculated values. This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on. In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are within tolerance. Therefore, we believe that FRQ model can accurately describe DAG framework.
}

>>>>

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
the FRQ model quantifies computing and I/O resources and displays them in time dimension. According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on. Therefore the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance. We will first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
The current distributed data parallel computing frameworks mostly use \textit{Directed Acyclic Graphs} (DAGs) to describe computation logic. A shuffle phase is required between each adjacent DAG computation phases. In order to better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model. After quantifying computing and I/O resources, the FRQ model is able to describe different resource scheduling strategies. For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. The FRQ model has five input parameters:
\begin{itemize}
	\item Input Data Size \((D)\): The data size of the computation phase.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase using the current computation resources. The number of rounds depends on the current computation resources and the settings of the computation job. Taking Hadoop MapReduce as an example, supposing we have 50 CPUs and enough memory, the map phase consists of 200 map tasks. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
    The computation speed for each computation phase. The computation speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
    Transmission speed during shuffle. Shuffle speed depends on network and storage device bandwidth.
\end{itemize}

@@

For shuffle-heavy computing jobs, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\). Improving I/O speed is an effective way to reduce shuffle time. Another optimization method is to use the idle I/O resources in the map phase for pre-fetching (see Figure \ref{fig:model_basic}). Both of the above methods can effectively reduce \(T_{P\_Shuffle}\). When using the FRQ model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework. Different computing frameworks may use different resource scheduling strategies. The FRQ model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.

@@

The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a naive scheduling strategy. As shown in Figure \ref{fig:model_original}, the FRQ model describes a MapReduce job that is fully serially executed. The overlap time between the shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\). Therefore, the overhead of the reduce phase is 0. But since shuffle and computation are serial execution, the total execution time of a job is different from the above:
\begin{equation}
\label{equation_Tjob2}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
\end{aligned}
\end{equation}
Apache Spark uses this scheduling strategy by default. Due to serialization, the I/O resource is idle during the reduce phase and map phase. The scheduling strategy is simple and has a lot of room for optimization.

Figure \ref{fig:model_hadoop} shows one of the optimization methods. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}). The execution time of the shuffle phase is hidden in the reduce phase. This scheduling strategy is used by Hadoop MapReduce. After analyzing this model, we believe that this strategy will be more efficient than the above serial strategy in the same situation. Meanwhile, we found that the I/O resource in the map phase is still idle. This scheduling strategy can be optimized.

@@

Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources. We intuitively think that we can also overlap shuffle phase one and map phases. We implemented this idea with SCache.
Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4). SCache starts pre-fetching and pre-scheduling in the map phase. This scheduling strategy can make better use of resources and avoid the I/O resource being idle in the map phase. According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

\begin{enumerate}
    \item 
    \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1}): 
	The meaning of \(V_{Map} \times R\) is the speed at which shuffle data is generated. The meaning of the inequality is that the speed of generating shuffle data(\(V_{Map} \times R\)) is greater than or equal to the shuffle speed(\(V_{Shuffle}\)). When the Round1 of the map phase ends, the SCache starts shuffling data until the end of the shuffle phase. Due to shuffle speed is slower, the shuffle phase is uninterrupted. SCache transmits the shuffle data generated in the last round of map phase during the reduce phase. Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase:
	\begin{equation}
		\label{equation_Tpshuffle1}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N}
		\end{aligned}
	\end{equation}

    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2}): 
	When the speed of generating shuffle data (\(V_{Map} \times R\)) is less than the shuffle speed (\(V_{Shuffle}\)), SCache needs to wait for shuffle data to be generated. As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each Round. Thus \(T_{P\_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase:
	\begin{equation}
		\label{equation_Tpshuffle2}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} \times \frac{1}{N}
		\end{aligned}
	\end{equation}
\end{enumerate}

@@

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
\label{table1}
\centering
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
\hline
 &
\(D\) &	
\(R\) &	
\(N\) &	
\(V_{Map}\) &	
\(V_{Reduce}\) &	
\(V_{Shuffle}\) &	
\(K\) &	
\(T_{Map}\) &	
\(T_{Shuffle}\) &	
\(T_{P\_Shuffle}\) &
\(T_{Reduce}\) & 
\(T_{Job}\) & 
\(Exp T_{Job}\) &
\(Error\)\\

@@

\renewcommand{\arraystretch}{1.3}
\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
\label{table2}
\centering
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
\hline
 &
\(D\) &	
\(R\) &	
\(N\) &	
\(V_{Map}\) &	
\(V_{Reduce}\) &	
\(V_{Shuffle}\) &	
\(K\) &	
\(T_{Map}\) &	
\(T_{Shuffle}\) &	
\(T_{P\_Shuffle}\) &
\(T_{Reduce}\) & 
\(T_{Job}\) & 
\(Exp T_{Job}\) &
\(Error\)\\

@@

\subsection{Model Verification}\label{model_verification}
In order to verify the FRQ model, we run experiments on two environments. The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Subsection \ref{stepup}. Another in-house environment has 4 nodes and each node has 128GB memory and 32 cores. To simplify the calculation of the FRQ model, we use Hadoop MapReduce as a framework and use Terasort as an experimental application. We deployed Hadoop with SCache and without SCache in both environments.

Table \ref{table1} shows the calculational results of the FRQ model in the in-house environment. Workload is from 16 GB to 64 GB. \(D\) and \(N\) are set according to the application parameters. \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are calculated based on experimental results. K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase in the case of SCache. The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. In the case of SCache, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}. In the case of Legacy, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}). \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\). The formula of \(Error\) is:
\begin{equation}
	\label{equation_error}
	\begin{aligned}
		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
	\end{aligned}
\end{equation}

Table \ref{table2} shows the calculational results of the FRQ model in Amazon EC2 environment. \(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices. We also set K to the same empirical value. The formulas in the table are all the same except \(T_{P\_Shuffle}\). In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}. In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).

@@

In order to verify the above-mentioned two cases when using SCache, we monitor network utilization and plot it in Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment. The network utilization remains high until the shuffle phase is completed. This situation is consistent with Figure \ref{fig:model_scache1}. Figure \ref{fig:hadoop_net2} shows the utilization in Amazon EC2 environment. 
The network utilization has 5 regular peaks. This situation is also consistent with Figure \ref{fig:model_scache2}. Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.

In terms of accuracy, the experimental values are all greater than the calculated values. This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on. In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are within tolerance. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
}

### 2018-10-17 tex/motivation.tex
Version 2.2
SongTao revision.

%In short, shuffle is loosely coupled with application context and it's I/O intensive.
\textbf{Impact of shuffle process}. Shuffle is I/O intensive, which might introduces a significant latency to the application. 
Reports show that 60\% of MapReduce jobs at Yahoo! and 20\% at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% JCT on average, up to 70\% in shuffle-heavy jobs \cite{managing}.
% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.

@@

\subsubsection{Inefficient Persistent Storage Operation}
At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking I/O operation. 
This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in an I/O performance bounded cluster.
Besides, the legacy of storing shuffle data on disk is inefficient in modern clusters with large memory. 
Compared to input dataset, the size of shuffle data is relatively small. 
For example, the shuffle size of Spark Terasort\footnote{https://github.com/ehiggs/spark-terasort} is less than 25\% of input data. 
The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as 10\%-20\%. 
On the other hand, memory based distributed storage systems have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory, 
but most of the DAG frameworks still store shuffle data on disks (e.g., Spark \cite{apachespark}, Hadoop MapReduce, Dryad \cite{dryad}, etc).
We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.

>>>>

%In short, shuffle is loosely coupled with application context and it's I/O intensive.
\textbf{Impact of shuffle process}. Shuffle is I/O intensive, which might introduce a significant latency to the application. 
Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.

@@

\subsubsection{Inefficient Persistent Storage Operation}
At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking I/O operation. 
This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in an I/O performance bounded cluster.
Besides, the legacy of storing shuffle data on disk is inefficient in modern clusters with large memory. 
Compared to input dataset, the size of shuffle data is relatively small. 
For example, the shuffle size of Spark Terasort\footnote{https://github.com/ehiggs/spark-terasort} is less than $25\%$ of input data. 
The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as $10\%-20\%$. 
On the other hand, memory based distributed storage systems have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory, 
but most of the DAG frameworks still store shuffle data on disks (e.g., Spark \cite{apachespark}, Hadoop MapReduce, Dryad \cite{dryad}, etc).
We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.
